Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-02 Dissertation/Thesis/tex/pogm.tex
figure captions in chap 2 updated for caption, then description, better for frontmatter

We propose a computational algorithm to evaluate \refeqn{InvSenModWithProbDens} efficiently. 
Since the cells outside of the sensor field of view (FOV) are not affected, we focus on a reduced map $r_l$ in the FOV of the $l$-th ray. This reduced map is chosen such that each cell of $r_l$ corresponds to a grid cell of map $m$ that the $l$-th ray intersects, ordered by increasing distance. Let $\mathbf{r}_{l,k}$ be the binary random variable representing the occupancy of the $k$-th cell of the $l$-th ray. The number of cells in the reduced map is denoted by $n_{r,l}\leq n_m$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_1.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_2.png}  
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_3.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_4.png}
  \caption{A robot located to the left of a 1D occupancy grid map $r_l$ composed of $n_{r,l}=6$ grid cells in four cases. In each case, cells the first three cells are free, the fourth cell is occupied, and the fifth and sixth cells may or may not be occupied. All above outcomes correspond to the event $\mathbf{r}_{l,4+}$.}
  \label{fig:show_rkplus}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{RayCastingIllustration.png}
        \caption{Ray Casting on a 2D Grid}
%        \label{fig:penn_map_total}
    \end{subfigure}
    \hspace*{0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{RayCastIllustrationReducedMapOnly.png}
        \caption{Reduced Map Only}
%        \label{fig:penn_map_zoom}
    \end{subfigure}
    \caption{This simple 2D example illustrates how ray casting determines the cells that compose the reduced map for the inverse sensor model. The closest edges are used to determine which cells should be considered, and in what order. The complete map cell indices are temporarily saved as well, which are used to associate probabilities to cells of the reduced map.}
    \label{fig:RayCastingIllustration}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.8\columnwidth}
        \centering
        \includegraphics[trim={1.5cm 3.5cm 1.5cm 1.5cm},clip,width=\textwidth]{map_comparison.png}
        \caption{Comparison of the total mapped environment based on the approximate (left) and proposed (right) inverse sensor model.}
        \label{fig:penn_map_total}
    \end{subfigure}
    \begin{subfigure}[t]{0.8\columnwidth}
        \centering
        \includegraphics[trim={1.5cm 3.5cm 1.5cm 1.5cm},clip,width=\textwidth]{map_zoom.png}
        \caption{Evidence of significant improvement at certain area of the map.}
        \label{fig:penn_map_zoom}
    \end{subfigure}
    \caption{Using experimental sensor data, the map was generated using an approximate and the proposed exact inverse sensor models. The laser sensor and odometry data used for the experiment was provided by University of Pennsylvania open course robotics estimation and learning on Coursera~\cite{coursera}.}
    \label{fig:penn_map}
\end{figure}

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.35\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_inf_19.pdf}
        \caption{Approximate inverse sensor model}
        \label{fig:AISM}
    \end{subfigure}
    \begin{subfigure}[t]{0.35\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_inf_19.pdf}
        \caption{Exact inverse sensor model}
        \label{fig:EISM}
    \end{subfigure}
    \caption{The entropy is compared between the approximate and proposed exact inverse sensor models at step 2280. The blue areas show the lowest entropy while red shows highest.}
    \label{fig:entropy_comp}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{entropy_frame.png}
  \caption{The map entropies of the approximate inverse sensor model (blue) and the proposed exact inverse sensor model (red) show that the exact version yields a more certain occupancy grid map.}
  \label{fig:entropy}
\end{figure}

@@

\begin{figure}
%    \centering{
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=0.7\columnwidth]{Compare_ISM_1.png}
%        \caption{Map at $t=0$ sec (exact)}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=0.7\columnwidth]{Compare_Approx_1.png}
%        \caption{Map at $t=0$ sec (approx.)}
%    \end{subfigure}
%    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_2.png}
        \caption{Map at $t=13$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_2.png}
        \caption{Map at $t=13$ sec (approx.)}
    \end{subfigure}
    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_3.png}
        \caption{Map at $t=25$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_3.png}
        \caption{Map at $t=25$ sec (approx.)}
    \end{subfigure}
    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_4.png}
        \caption{Map at $t=38$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_4.png}
        \caption{Map at $t=38$ sec (approx.)}
    \end{subfigure}
    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_5.png}
        \caption{Map at $t=50$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_5.png}
        \caption{Map at $t=50$ sec (approx.)}
    \end{subfigure}
    }
\caption{A robot (green crossed circle, green curve of its previous $13$ seconds) measures a room with a Kinect depth sensor. The exact inverse sensor model is compared with an approximate algorithm designed for the Kinect depth sensor. Grid cells are either known as free (white) or occupied (black), or uncertain with a grayscale color.
%The exact inverse sensor model approach generates a more accurate result.
}
\label{fig:NumResOccProbs}
\end{figure}

@@

\begin{figure}
    \centering{
    \begin{subfigure}[t]{0.8\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{EntropyEvolution.png}
        \caption{Entropy (black: exact model, green: approx.)}
        \label{fig:NumResOccHa}
    \end{subfigure}
}
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_H.png}
        \caption{Entropy map at $t=50$ (exact)}
        \label{fig:NumResOccHb}
    \end{subfigure}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_H.png}
        \caption{Entropy map at $t=50$  (approx.)}
        \label{fig:NumResOccHc}
    \end{subfigure}
    }
\caption{Entropy serves as a measure of uncertainty of the occupancy grid, where more blue regions are more certain, and red regions are more uncertain. The uncertainty is always less when the exact solution is applied.}\label{fig:NumResOccH}
\end{figure}

>>>>

We propose a computational algorithm to evaluate \refeqn{InvSenModWithProbDens} efficiently~\cite{KauLeeAiMos16,KauTakAiLee17}. 
Since the cells outside of the sensor field of view (FOV) are not affected, we focus on a reduced map $r_l$ in the FOV of the $l$-th ray. This reduced map is chosen such that each cell of $r_l$ corresponds to a grid cell of map $m$ that the $l$-th ray intersects, ordered by increasing distance. Let $\mathbf{r}_{l,k}$ be the binary random variable representing the occupancy of the $k$-th cell of the $l$-th ray. The number of cells in the reduced map is denoted by $n_{r,l}\leq n_m$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_1.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_2.png}  
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_3.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_4.png}
  \caption{Occupancy Grid Maps with Identical Forward Sensor Models}
  \medskip
  \small
  A robot located to the left of a 1D occupancy grid map $r_l$ composed of $n_{r,l}=6$ grid cells in four cases. In each case, cells the first three cells are free, the fourth cell is occupied, and the fifth and sixth cells may or may not be occupied. All above outcomes correspond to the event $\mathbf{r}_{l,4+}$.
  \label{fig:show_rkplus}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{RayCastingIllustration.png}
        \caption{Ray Casting on a 2D Grid}
%        \label{fig:penn_map_total}
    \end{subfigure}
    \hspace*{0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{RayCastIllustrationReducedMapOnly.png}
        \caption{Reduced Map Only}
%        \label{fig:penn_map_zoom}
    \end{subfigure}
    \caption{Ray Casting Illustration}
    \label{fig:RayCastingIllustration}
    	\medskip
  	\small
	This simple 2D example illustrates how ray casting determines the cells that compose the reduced map for the inverse sensor model. The closest edges are used to determine which cells should be considered, and in what order. The complete map cell indices are temporarily saved as well, which are used to associate probabilities to cells of the reduced map.
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.8\columnwidth}
        \centering
        \includegraphics[trim={1.5cm 3.5cm 1.5cm 1.5cm},clip,width=\textwidth]{map_comparison.png}
        \caption{Comparison of the total mapped environment based on the approximate (left) and proposed (right) inverse sensor model.}
        \label{fig:penn_map_total}
    \end{subfigure}
    \begin{subfigure}[t]{0.8\columnwidth}
        \centering
        \includegraphics[trim={1.5cm 3.5cm 1.5cm 1.5cm},clip,width=\textwidth]{map_zoom.png}
        \caption{Evidence of significant improvement at certain area of the map.}
        \label{fig:penn_map_zoom}
    \end{subfigure}
    \caption{Comparison of Proposed Ray-By-Ray Approach with Approximate Solution}
	\medskip
	\small
	Using experimental sensor data, the map was generated using an approximate and the proposed exact inverse sensor models. The laser sensor and odometry data used for the experiment was provided by University of Pennsylvania open course robotics estimation and learning on Coursera~\cite{coursera}.
    \label{fig:penn_map}
\end{figure}

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.35\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_inf_19.pdf}
        \caption{Approximate inverse sensor model}
        \label{fig:AISM}
    \end{subfigure}
    \begin{subfigure}[t]{0.35\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_inf_19.pdf}
        \caption{Exact inverse sensor model}
        \label{fig:EISM}
    \end{subfigure}
    \caption{Map Uncertainty Comparison Between Proposed Ray-By-Ray Approach and Approximate Solution}
	\medskip
	\small
	The entropy is compared between the approximate and proposed exact inverse sensor models at step 2280. The blue areas show the lowest entropy while red shows highest.
\label{fig:entropy_comp}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{entropy_frame.png}
  \caption{Entropy Histories of the Proposed Ray-By-Ray Approach and Approximate Solution}
  	\medskip
	\small
	The map entropies of the approximate inverse sensor model (blue) and the proposed exact inverse sensor model (red) show that the exact version yields a more certain occupancy grid map.
\label{fig:entropy}
\end{figure}

@@

\begin{figure}
%    \centering{
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=0.7\columnwidth]{Compare_ISM_1.png}
%        \caption{Map at $t=0$ sec (exact)}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=0.7\columnwidth]{Compare_Approx_1.png}
%        \caption{Map at $t=0$ sec (approx.)}
%    \end{subfigure}
%    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_2.png}
        \caption{Map at $t=13$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_2.png}
        \caption{Map at $t=13$ sec (approx.)}
    \end{subfigure}
    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_3.png}
        \caption{Map at $t=25$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_3.png}
        \caption{Map at $t=25$ sec (approx.)}
    \end{subfigure}
    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_4.png}
        \caption{Map at $t=38$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_4.png}
        \caption{Map at $t=38$ sec (approx.)}
    \end{subfigure}
    }
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_5.png}
        \caption{Map at $t=50$ sec (exact)}
    \end{subfigure}
    \hspace*{-0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_5.png}
        \caption{Map at $t=50$ sec (approx.)}
    \end{subfigure}
    }
    \caption{Comparison of Proposed Synergistic Approach with Approximate Solution}
	\medskip
	\small
	A robot (green crossed circle, green curve of its previous $13$ seconds) measures a room with a Kinect depth sensor. Grid cells are either known as free (white) or occupied (black), or uncertain (gray).
\label{fig:NumResOccProbs}
\end{figure}

@@

\begin{figure}
    \centering{
    \begin{subfigure}[t]{0.8\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{EntropyEvolution.png}
        \caption{Entropy (black: exact model, green: approx.)}
        \label{fig:NumResOccHa}
    \end{subfigure}
}
    \centering{
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_ISM_H.png}
        \caption{Entropy map at $t=50$ (exact)}
        \label{fig:NumResOccHb}
    \end{subfigure}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=0.7\columnwidth]{Compare_Approx_H.png}
        \caption{Entropy map at $t=50$  (approx.)}
        \label{fig:NumResOccHc}
    \end{subfigure}
    }
    \caption{Map Uncertainty Comparison Between Proposed Synergistic Approach and Approximate Solution}
	\medskip
	\small
	Entropy serves as a measure of uncertainty of the occupancy grid, where more blue regions are more certain, and red regions are more uncertain. The uncertainty is always less when the exact solution is applied.
\label{fig:NumResOccH}
\end{figure}

### 2018-07-02 Dissertation/Thesis/tex/results.tex
figure captions in chap 2 updated for caption, then description, better for frontmatter

\paragraph{Hardware Configuration}
The Pioneer 3 ground robot is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provide the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

\paragraph{Software Configuration}

@@

\paragraph{Exploring and Mapping a 2D Environment}
The environment consists of Styrofoam walls on a flat floor. The perimeter is rectangular, with several obstacles and angled walls (see Figure \ref{fig:ExpSetupPhoto}). The robot autonomously explored the space using the complete Cartesian searching approach, and Dijkstra's algorithm provides collision-free waypoints to the optimal future poses. Based on these waypoints, a constrained least squares polynomial fitting generates a smooth trajectory to follow the waypoints with fixed velocity. Finally, a simple controller is implemented such that the Pioneer follows the trajectory by moving and orienting toward the desired robot location $1$ sec in the future.

>>>>

\subsection{Hardware Configuration}
The Pioneer 3 ground robot is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provide the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

\subsection{Software Configuration}

@@

\subsection{Exploring and Mapping a 2D Environment}
The environment consists of Styrofoam walls on a flat floor. The perimeter is rectangular, with several obstacles and angled walls (see Figure \ref{fig:ExpSetupPhoto}). The robot autonomously explored the space using the complete Cartesian searching approach, and Dijkstra's algorithm provides collision-free waypoints to the optimal future poses. Based on these waypoints, a constrained least squares polynomial fitting generates a smooth trajectory to follow the waypoints with fixed velocity. Finally, a simple controller is implemented such that the Pioneer follows the trajectory by moving and orienting toward the desired robot location $1$ sec in the future.
